04_DESeq_gon

### 2019-04-07 analysis/02_DESeq2_hyp.Rmd
better legends and axis labels

ggplot(dat, aes(V1, V2)) +
  geom_tile(aes(fill = V3)) +
  scale_fill_viridis(na.value="#FFFFFF00") + 
  xlab("Treatment") + ylab("Treatment") +
  labs(fill = "# of DEGs")
```

@@

ggplot(dat, aes(V1, V2)) +
  geom_tile(aes(fill = V3)) +
  scale_fill_viridis(na.value="#FFFFFF00") + 
  xlab("Treatment") + ylab("Treatment") +
  labs(fill = "# of DEGs")
```

>>>>

ggplot(dat, aes(V1, V2)) +
  geom_tile(aes(fill = V3)) +
  scale_fill_viridis(na.value="#FFFFFF00", 
                     limits = c(0,8028),
                     breaks = c(0, 2000, 4000, 6000, 8000)) + 
  xlab("Timepoint") + ylab("Timepoint") +
  labs(fill = "# of DEGs")
```

@@

ggplot(dat, aes(V1, V2)) +
  geom_tile(aes(fill = V3)) +
  scale_fill_viridis(na.value="#FFFFFF00", 
                     limits = c(0,8028),
                     breaks = c(0, 2000, 4000, 6000, 8000)) + 
  xlab(" ") + ylab("Timepoint") +
  labs(fill = "# of DEGs")
```

### 2019-04-07 analysis/03_DESeq2_pit.Rmd
better legends and axis labels

ggplot(dat, aes(V1, V2)) +
  geom_tile(aes(fill = V3)) +
  scale_fill_viridis(na.value="#FFFFFF00", 
                     limits = c(0,8028)) + 
  xlab("Timepoint") + ylab("Timepoint") +
  labs(fill = "# of DEGs")
```

@@

ggplot(dat, aes(V1, V2)) +
  geom_tile(aes(fill = V3)) +
  scale_fill_viridis(na.value="#FFFFFF00",
                     limits = c(0,8028)) + 
  xlab("Timepoint") + ylab("Timepoint") +
  labs(fill = "# of DEGs")
```

>>>>

ggplot(dat, aes(V1, V2)) +
  geom_tile(aes(fill = V3)) +
  scale_fill_viridis(na.value="#FFFFFF00", 
                     limits = c(0,8028),
                     breaks = c(0, 2000, 4000, 6000, 8000)) + 
  xlab("Timepoint") + ylab("Timepoint") +
  labs(fill = "# of DEGs")  
```

@@

ggplot(dat, aes(V1, V2)) +
  geom_tile(aes(fill = V3)) +
  scale_fill_viridis(na.value="#FFFFFF00", 
                     limits = c(0,8028),
                     breaks = c(0, 2000, 4000, 6000, 8000)) + 
  xlab(" ") + ylab("Timepoint") +
  labs(fill = "# of DEGs")  
```

### 2019-04-07 analysis/04_DESeq2_gon.Rmd
better legends and axis labels

ggplot(dat, aes(V1, V2)) +
  geom_tile(aes(fill = V3)) +
  scale_fill_viridis(na.value="#FFFFFF00") + 
  xlab("Treatment") + ylab("Treatment") +
  labs(fill = "# of DEGs")
```

>>>>

ggplot(dat, aes(V1, V2)) +
  geom_tile(aes(fill = V3)) +
  scale_fill_viridis(na.value="#FFFFFF00", 
                     limits = c(0,8028),
                     breaks = c(0, 2000, 4000, 6000, 8000)) + 
  xlab(" ") + ylab("Timepoint") +
  labs(fill = "# of DEGs")

dat %>%
  filter(V1 != "control")  %>%
  ggplot( aes(V1, V2)) +
    geom_tile(aes(fill = V3)) +
    scale_fill_viridis(na.value="#FFFFFF00", 
                     limits = c(0,8028),
                     breaks = c(0, 2000, 4000, 6000, 8000)) + 
    xlab(" ") + ylab("Timepoint") +
    labs(fill = "# of DEGs")
```
